---
title: "boosting"
author: "ajing"
date: "04/03/2015"
output: html_document
---

Cleaning and some basic operation on data
```{r}
train_data <- read.csv("./Data/train.csv")
test_data  <- read.csv("./Data/test.csv")
train_data$Open.Date = as.numeric(as.Date(train_data$Open.Date, "%m/%d/%Y"))
test_data$Open.Date = as.numeric(as.Date(test_data$Open.Date, "%m/%d/%Y"))
levels(train_data$Type) = levels(test_data$Type)
levels(train_data$City) = levels(test_data$City)
```

revenue cut for correction
```{r}
revenue_cut = 7e6
train_data$revenue.c = factor(c("small", "large") [ 1 + (train_data$revenue > revenue_cut)])
```

remove the outlier
```{r}
train_data = subset(train_data, revenue < 1e7)
```

Only keep first 5 PCA (sd > 1)
```{r}
train_pca <- prcomp(train_data[, grepl( "P+" , names(train_data))], center = TRUE, scale = TRUE) 
train_lowdim= cbind(train_data[, !grepl( "P+" , names(train_data))], predict(train_pca)[,1:5])
```

Testing set dimension reduction
```{r}
test_lowdim = cbind(test_data[, !grepl( "P+" , names(test_data))], predict(train_pca, newdata = test_data[, grepl( "P+" , names(test_data))])[,1:5])
```

SVM for small/large revenue assignment
```{r}
library('e1071')
obj <- tune.svm(revenue.c~., data = subset(train_lowdim, select = !(colnames(train_lowdim) %in% c("Id", "revenue"))), gama = 2^(-10:1), cost = 2^(2:10))
model <- obj$best.model
pre_result_train <- predict(model, subset(train_lowdim,select = Open.Date:PC5))
svm_se = sqrt(sum((pre_result_train == train_data$revenue.c)^2)/ length(train_data$revenue))

```

random forest for group assignment
```{r}
model_s <- randomForest(revenue.c~., data = subset(train_lowdim, select = !(colnames(train_lowdim) %in% c("Id", "revenue", "City", "revenue.g"))), ntree = 100, maxnodes = 15)
pre_result_train <- predict(model_s, subset(train_lowdim,select = Open.Date:PC5))
train_lowdim$revenue.g <- predict(model_s, subset(train_lowdim,select = Open.Date:PC5))
table(pre_result_train, train_data$revenue.c)
```



randomForest
```{r}
library("randomForest")
get_model <- function(train_lowdim){
  model <- randomForest(revenue~.,data=subset(train_lowdim, select = !(names(train_lowdim) %in% c("Id", "City", "revenue.c"))), importance = T, ntree = 10, maxnodes = 5)
  pre_result_train <- predict(model, subset(train_lowdim,select = Open.Date:PC5))
  print(sqrt(sum((pre_result_train - train_lowdim$revenue)^2)/ length(train_lowdim$revenue)))
  model
}
model_small  <- get_model(subset(train_lowdim, revenue < revenue_cut))
model_large  <- get_model(subset(train_lowdim, revenue > revenue_cut))

model  <- get_model(train_lowdim)

model  <- get_model(subset(train_lowdim, select = -revenue.g))

predict_with_model <- function(test_lowdim){
pre_rev_result <- predict(model, subset(test_lowdim, select = !(names(test_lowdim) %in% c("Id", "City", "revenue.c"))))
pre_result <- matrix(0, dim(test_lowdim)[1], 1)
pre_result[pre_rev_result == "large",] <- predict(model_large, subset(test_lowdim[pre_rev_result == "large", ], select = -Id))
pre_result[pre_rev_result == "small",] <- predict(model_small, subset(test_lowdim[pre_rev_result == "small", ], select = -Id))
pre_result
}
pre_result <- predict_with_model(train_lowdim)
plot(pre_result, train_lowdim$revenue)

library(gdata)
pre_result <- unmatrix(predict_with_model(test_lowdim))
```

normal randomForest
```{r}
library("randomForest")
model <- randomForest(revenue~.,data=subset(train_lowdim, select = !(names(train_lowdim) %in% c("Id", "City"))), importance = T, ntree = 200, maxnodes = 20)
pre_result_train <- predict(model, subset(train_lowdim,select = Open.Date:PC5))
sqrt(sum((pre_result_train - train_data$revenue)^2)/ length(train_data$revenue))
plot(pre_result_train, train_data$revenue)
abline(a=0,b=1)
pre_result <- predict(model, subset(test_lowdim, select = -Id))
```


SVM as 2-level model
```{r}
get_model <- function(train_lowdim){
  model <- svm(revenue~.,data=subset(train_lowdim, select = !(names(train_lowdim) %in% c("Id", "City", "revenue.c"))))
  pre_result_train <- predict(model, subset(train_lowdim,select = Open.Date:PC5))
  print(sqrt(sum((pre_result_train - train_lowdim$revenue)^2)/ length(train_lowdim$revenue)))
  model
}
model_small  <- get_model(subset(train_lowdim, revenue <= revenue_cut))
model_large  <- get_model(subset(train_lowdim, revenue > revenue_cut))


predict_with_model <- function(test_lowdim){
pre_rev_result <- predict(model, subset(test_lowdim, select = !(names(test_lowdim) %in% c("Id", "City", "revenue.c"))))
pre_result <- matrix(0, dim(test_lowdim)[1], 1)
pre_result[pre_rev_result == "large",] <- predict(model_large, subset(test_lowdim[pre_rev_result == "large", ], select = -Id))
pre_result[pre_rev_result == "small",] <- predict(model_small, subset(test_lowdim[pre_rev_result == "small", ], select = -Id))
pre_result
}
pre_result <- predict_with_model(train_lowdim)
plot(pre_result, train_lowdim$revenue)
abline(a=0,b=1)
```



randomForest with one more attribute revenue.g
```{r}
get_model <- function(train_lowdim){
  model <- svm(revenue~.,data=subset(train_lowdim, select = !(names(train_lowdim) %in% c("Id", "City", "revenue.c"))))
  pre_result_train <- predict(model, subset(train_lowdim, select = !(names(train_lowdim) %in% c("Id", "City", "revenue.c"))))
  print(sqrt(sum((pre_result_train - train_lowdim$revenue)^2)/ length(train_lowdim$revenue)))
  model
}
model  <- get_model(train_lowdim)
pre_result <- predict(model, train_lowdim)
plot(pre_result, train_lowdim$revenue)
abline(a=0,b=1)


test_lowdim$revenue.g <- predict(model_s, subset(test_lowdim,select = Open.Date:PC5))
pre_result <- predict(model, test_lowdim)


model <- randomForest(revenue~.,data=subset(train_lowdim, select = !(names(train_lowdim) %in% c("Id", "City", "revenue.c"))), importance = T, ntree = 100, maxnodes = 10)
pre_result_train <- predict(model, subset(train_lowdim,select = !(names(train_lowdim) %in% c("Id", "City"))))
sqrt(sum((pre_result_train - train_data$revenue)^2)/ length(train_data$revenue))
plot(pre_result_train, train_lowdim$revenue)
abline(a=0,b=1)

pre_result <- predict(model, test_lowdim)

```


Gradient Boosted Trees

```{r}
library("gbm")
model <- gbm(revenue~.,data=subset(train_data, select = !(names(train_data) %in% c("Id", "City"))), n.trees=1000, interaction.depth=3)
pre_result_train <- predict.gbm(model, subset(train_data,select = Open.Date:P37), type="response", n.trees = 1000)
sqrt(sum((pre_result_train - train_data$revenue)^2)/ length(train_data$revenue))

pre_result <- predict.gbm(model, test_data, type="response", n.trees=100)
```



Save prediction to file
```{r}
write.csv(cbind(Id = test_data$Id, Prediction = pre_result), quote = F, row.names = F, file = "./predict_result.csv")
```

